---
title: "Transform Equivalence - Parameter Study Compare Representations; exp addendum gamma-free, Study 4"
subtitle: "Watkins Q, Linear Function Approximation"
author: Simon C Stanton
date: "`r format(Sys.time(), '%d %B %Y')`"
params:
  algorithm: watkins_q_lfa
  algorithm_displayname: "Watkins Q, Linear Function Approximation"
  exp_id_transform_one: 129758
  exp_id_transform_two: 133215 
  transform_one: "ordinal"
  transform_two: "ordinal_norm.3"
output:
  pdf_document: default
  html_document: default
knit: (function(inputFile, encoding) { 
        rmarkdown::render(inputFile, 
                          encoding = encoding, 
                          output_file = paste(file.path(dirname(inputFile), "pdfs/", "compare_transforms__parameter_study__EXP_ADDENDUM_S4__watkins_q_lfa__ordinal_ordinal_norm3-test.pdf")))
      })
---
\newpage

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#rmarkdown::render('Parameter_Study_Compare_Representation.Rmd', output_file = paste('report.', Sys.Date(), '.pdf', sep=''))

library(ggplot2)
library(car)
library(ggpubr)


```

```{r, import-data, echo=FALSE, include=FALSE}
path_to_data = "C:/Users/__USER__/Desktop/kunanyi/results/observations/selfplay_parameter_study/"
view_path = "/view/ep_o/view_"
file_suffix_pre = "_ep_o_table_parameter_study_"
file_suffix_post = "_series.csv"

exp_id_transform_one <- params$exp_id_transform_one 
exp_id_transform_two <- params$exp_id_transform_two

transform_one <- params$transform_one
transform_two <- params$transform_two

strategy <- params$algorithm_displayname 
strategy_filename <- params$algorithm 


# transform_one

## CC Series
filename = paste(path_to_data, exp_id_transform_one, view_path, exp_id_transform_one, file_suffix_pre, "cc", file_suffix_post, sep="")
df_transform_one_set_cc <- read.csv(file= filename, header=TRUE)

## CD Series
filename = paste(path_to_data, exp_id_transform_one, view_path, exp_id_transform_one, file_suffix_pre, "cd", file_suffix_post, sep="")
df_transform_one_set_cd <- read.csv(file= filename, header=TRUE)

## DC Series
filename = paste(path_to_data, exp_id_transform_one, view_path, exp_id_transform_one, file_suffix_pre, "dc", file_suffix_post, sep="")
df_transform_one_set_dc <- read.csv(file= filename, header=TRUE)

## DD Series
filename = paste(path_to_data, exp_id_transform_one, view_path, exp_id_transform_one, file_suffix_pre, "dd", file_suffix_post, sep="")
df_transform_one_set_dd <- read.csv(file= filename, header=TRUE)

# Ordinal 

## CC Series
filename = paste(path_to_data, exp_id_transform_two, view_path, exp_id_transform_two, file_suffix_pre, "cc", file_suffix_post, sep="")
df_transform_two_set_cc <- read.csv(file= filename, header=TRUE)

## CD Series
filename = paste(path_to_data, exp_id_transform_two, view_path, exp_id_transform_two, file_suffix_pre, "cd", file_suffix_post, sep="")
df_transform_two_set_cd <- read.csv(file= filename, header=TRUE)

## DC Series
filename = paste(path_to_data, exp_id_transform_two, view_path, exp_id_transform_two, file_suffix_pre, "dc", file_suffix_post, sep="")
df_transform_two_set_dc <- read.csv(file= filename, header=TRUE)

## DD Series
filename = paste(path_to_data, exp_id_transform_two, view_path, exp_id_transform_two, file_suffix_pre, "dd", file_suffix_post, sep="")
df_transform_two_set_dd <- read.csv(file= filename, header=TRUE)



df_combined_transforms <- data.frame(
    Index <- c(seq.int(400), seq.int(400)),
    Representation = factor(c(rep(paste(transform_one), 400), rep(paste(transform_two), 400))),
    Outcome = factor(c(rep("CC", 100), rep("CD", 100), rep("DC", 100), rep("DD", 100), rep("CC", 100), rep("CD", 100), rep("DC", 100), rep("DD", 100))),
    Proportion = c(df_transform_one_set_cc$CC, df_transform_one_set_cd$CD, df_transform_one_set_dc$DC, df_transform_one_set_dd$DD,  df_transform_two_set_cc$CC, df_transform_two_set_cd$CD, df_transform_two_set_dc$DC, df_transform_two_set_dd$DD)
)

# swaps order of transforms in boxplot by using levels() - factor() is by default alphabetical
df_combined_transforms$Representation <- factor(df_combined_transforms$Representation, levels=c(paste(transform_one), paste(transform_two)))


```

# Visualise Data 

## Grouped Boxplot

```{r, echo=FALSE}
ggplot(df_combined_transforms, aes(x=Representation, y=Proportion, fill=Outcome)) + 
  geom_boxplot() + 
  coord_cartesian(ylim = c(0, 1)) + 
  theme_bw() + 
  scale_color_grey() + 
  scale_fill_brewer(palette="Blues") + 
  #annotate("text", x = Inf, y = -0.01, label = paste("exp_", exp_id_transform_one, " x ","exp_", exp_id_transform_two, sep=""), hjust=2.5, vjust=0.8, col="black", cex=3, alpha = 0.3) +
  labs(title = paste(strategy, "Paired Parameter Study", sep=" "),
        subtitle = paste("Distribution of ", transform_one, " & ", transform_two, " outcomes. Exp IDs: ", exp_id_transform_one, ", ", exp_id_transform_two, sep="")) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12),    # Center title position and size
    plot.subtitle = element_text(hjust = 0.5, size=10),            # Center subtitle
    plot.caption = element_text(hjust = 0, face = "italic") # move caption to the left
  ) 

# #caption = "Distribution of scalar and ordinal outcomes in Prisoner's Dilemma parameter study across scalar\nand ordinal representation.") +
# Outcomes are labelled as CC (Mutual Cooperation), CD (Cooperate/Defect),\nDC (Defect/Cooperate), DD (Mutual Defection). Each experiment comprised 500 episodes of 1000 timesteps each.\nProportion, or frequency of an outcome is the average of each parameter pairing of $\alpha, \beta over range (0.1, 1.0)

ggsave(path="plots", filename=paste("compare_transforms_", strategy_filename, "_", exp_id_transform_one, "_", exp_id_transform_two, "_grouped_boxplot-test.png", sep=""), width=8, height=6, dpi=300) 
  
```

## Facet Boxplot with paired lines

```{r, echo=FALSE}

ggplot(df_combined_transforms, aes(x = Representation, y = Proportion)) +
    geom_boxplot(aes(fill = Representation)) +
    geom_point(aes(col = Representation, group=Index), size = 0.3, stroke = 0, shape = 16) +
    geom_line(aes(group = Index),alpha = 0.2, col = "grey", size = 0.3) +
    facet_wrap(df_combined_transforms$Outcome) +
  coord_cartesian(ylim = c(0, 1))  +
  stat_compare_means(paired=TRUE, label.x = 1.35, label.y = 0.9) +
    #labs(title = paste(strategy, "Paired Parameter Study", sep=" "),
  labs(title = paste(strategy, "Paired Treatment", sep=" "),
        subtitle = paste("Distribution of ", transform_one, " & ", transform_two, " outcomes. [Exp IDs: ", exp_id_transform_one, ", ", exp_id_transform_two, "]", sep="")) +
  theme_minimal() +
  scale_fill_brewer(palette="Blues") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12),    # Center title position and size
    plot.subtitle = element_text(hjust = 0.5, size=10),            # Center subtitle
    plot.caption = element_text(hjust = 0, face = "italic") # move caption to the left
  ) +
  rremove("legend")

ggsave(path="plots", filename=paste("compare_transforms_", strategy_filename, "_", exp_id_transform_one, "_", exp_id_transform_two, "_facet_boxplot_paired_lines-test.png", sep=""), width=8, height=6, dpi=300, bg='white')
```

\newpage

# Test equality of variance within transform group, by outcome: H_0 variances are equal
## Transform One: `r transform_one` (Proportion ~ Outcome)

```{r, echo=FALSE}

# Test equality of variances: H_0 variances are equal
leveneTest(Proportion ~ Outcome, data=subset(df_combined_transforms, df_combined_transforms$Representation==paste(transform_one)))

```

## Transform Two: `r transform_two` (Proportion ~ Outcome)

```{r, echo=FALSE}
leveneTest(Proportion ~ Outcome, data=subset(df_combined_transforms, df_combined_transforms$Representation==paste(transform_two)))

```

\newpage

# Tests for Normal Distribution

## All Outcomes Aggregated

### `r transform_one`

```{r, echo=FALSE}

# All Outcomes squished to one vector

df_all_outcomes_transform_one <- subset(df_combined_transforms, df_combined_transforms$Representation==paste(transform_one))

boxplot(df_all_outcomes_transform_one$Proportion)

hist(df_all_outcomes_transform_one$Proportion)
plot(density(df_all_outcomes_transform_one$Proportion))

#qqPlot(df_all_outcomes_transform_one$Proportion)
ggqqplot(df_all_outcomes_transform_one$Proportion)

shapiro.test(df_all_outcomes_transform_one$Proportion)

```

### `r transform_two`

```{r, echo=FALSE}

# All Outcomes squished to one vector

df_all_outcomes_transform_two <- subset(df_combined_transforms, df_combined_transforms$Representation==paste(transform_two))

boxplot(df_all_outcomes_transform_two$Proportion)

hist(df_all_outcomes_transform_two$Proportion)
plot(density(df_all_outcomes_transform_two$Proportion))

#qqPlot(df_all_outcomes_transform_two$Proportion)
ggqqplot(df_all_outcomes_transform_two$Proportion)

shapiro.test(df_all_outcomes_transform_two$Proportion)

```

## Outcomes Disaggregated

### CC `r transform_one`
(Ignore histogram, plot titles etc, 'transform_one' etc are variables names, have not set titles)

```{r, echo=FALSE}

df_transform_one_cc <- subset(df_combined_transforms, df_combined_transforms$Representation==paste(transform_one) & df_combined_transforms$Outcome=="CC")

boxplot(df_transform_one_cc$Proportion)
hist(df_transform_one_cc$Proportion)
plot(density(df_transform_one_cc$Proportion))

#qqPlot(df_transform_one_cc$Proportion)
ggqqplot(df_transform_one_cc$Proportion)

shapiro.test(df_transform_one_cc$Proportion)

```

### CC `r transform_two`

```{r, echo=FALSE}


df_transform_two_cc <- subset(df_combined_transforms, df_combined_transforms$Representation==paste(transform_two) & df_combined_transforms$Outcome=="CC")

boxplot(df_transform_two_cc$Proportion)
hist(df_transform_two_cc$Proportion)
plot(density(df_transform_two_cc$Proportion))

#qqPlot(df_transform_two_cc$Proportion)
ggqqplot(df_transform_two_cc$Proportion)

shapiro.test(df_transform_two_cc$Proportion)


# Plot and test
```


### CD `r transform_one`

```{r, echo=FALSE}


df_transform_one_cd <- subset(df_combined_transforms, df_combined_transforms$Representation==paste(transform_one) & df_combined_transforms$Outcome=="CD")

boxplot(df_transform_one_cd$Proportion)
hist(df_transform_one_cd$Proportion)
plot(density(df_transform_one_cd$Proportion))

#qqPlot(df_transform_one_cd$Proportion)
ggqqplot(df_transform_one_cd$Proportion)

shapiro.test(df_transform_one_cd$Proportion)


```

### CD `r transform_two`

```{r, echo=FALSE}

df_transform_two_cd <- subset(df_combined_transforms, df_combined_transforms$Representation==paste(transform_two) & df_combined_transforms$Outcome=="CD")

boxplot(df_transform_two_cd$Proportion)
hist(df_transform_two_cd$Proportion)
plot(density(df_transform_two_cd$Proportion))

#qqPlot(df_transform_two_cd$Proportion)
ggqqplot(df_transform_two_cd$Proportion)

shapiro.test(df_transform_two_cd$Proportion)


# Plot and test
```


### DC `r transform_one`

```{r, echo=FALSE}


df_transform_one_dc <- subset(df_combined_transforms, df_combined_transforms$Representation==paste(transform_one) & df_combined_transforms$Outcome=="DC")

boxplot(df_transform_one_dc$Proportion)
hist(df_transform_one_dc$Proportion)
plot(density(df_transform_one_dc$Proportion))

#qqPlot(df_transform_one_dc$Proportion)
ggqqplot(df_transform_one_dc$Proportion)

shapiro.test(df_transform_one_dc$Proportion)
```

### DC `r transform_two`

```{r, echo=FALSE}


df_transform_two_dc <- subset(df_combined_transforms, df_combined_transforms$Representation==paste(transform_two) & df_combined_transforms$Outcome=="DC")

boxplot(df_transform_two_dc$Proportion)
hist(df_transform_two_dc$Proportion)
plot(density(df_transform_two_dc$Proportion))

#qqPlot(df_transform_two_dc$Proportion)
ggqqplot(df_transform_two_dc$Proportion)

shapiro.test(df_transform_two_dc$Proportion)


```



### DD `r transform_one`

```{r, echo=FALSE}


df_transform_one_dd <- subset(df_combined_transforms, df_combined_transforms$Representation==paste(transform_one) & df_combined_transforms$Outcome=="DD")

boxplot(df_transform_one_dd$Proportion)
hist(df_transform_one_dd$Proportion)
plot(density(df_transform_one_dd$Proportion))

#qqPlot(df_transform_one_dd$Proportion)
ggqqplot(df_transform_one_dd$Proportion)

shapiro.test(df_transform_one_dd$Proportion)

```

### DD `r transform_two`

```{r, echo=FALSE}


df_transform_two_dd <- subset(df_combined_transforms, df_combined_transforms$Representation==paste(transform_two) & df_combined_transforms$Outcome=="DD")

boxplot(df_transform_two_dd$Proportion)
hist(df_transform_two_dd$Proportion)
plot(density(df_transform_two_dd$Proportion))

#qqPlot(df_transform_two_dd$Proportion)
ggqqplot(df_transform_two_dd$Proportion)

shapiro.test(df_transform_two_dd$Proportion)

```



\newpage


# Tests for equivalence

## All Outcomes Aggregated
Wilcoxon test (paired difference test) for non-normal distributions. 
H_0: samples are drawn from populations with equivalent mean ranks.

### Boxplot

```{r, echo=FALSE}
# Plot and test

ggplot(df_combined_transforms, aes(x=Representation, y=Proportion)) + geom_boxplot() + coord_cartesian(ylim = c(0, 1)) + theme_bw()

```

### Wilcoxon

```{r, echo=FALSE}
wilcox.test(df_all_outcomes_transform_one$Proportion, df_all_outcomes_transform_two$Proportion, paired = TRUE, alternative = "two.sided", conf.int = TRUE, exact=FALSE)

```
### Aggregated outcomes by representation - boxplot with paired lines

```{r, echo=FALSE}

ggplot(df_combined_transforms, aes(x = Representation, y = Proportion)) +
    geom_boxplot(aes(fill = Representation)) +
    geom_point(aes(col = Representation), size = 0.1, stroke = 0, shape = 16) +
    geom_line(aes(group = Index),alpha = 0.2, col = "grey") +
  coord_cartesian(ylim = c(0, 1))  +
  stat_compare_means(paired=TRUE, label.x = 1.35, label.y = 0.95) +
    labs(title = paste(strategy, "Paired Parameter Study", sep=" "),
        subtitle = paste("Distribution of Aggregated ", transform_one, " & ", transform_two, " Outcomes. [Exp IDs: ", exp_id_transform_one, ", ", exp_id_transform_two, "]", sep="")) +
  theme_minimal() +
  scale_fill_brewer(palette="Blues") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12),    # Center title position and size
    plot.subtitle = element_text(hjust = 0.5, size=10),            # Center subtitle
    plot.caption = element_text(hjust = 0, face = "italic") # move caption to the left
  ) +
  rremove("legend")

ggsave(path="plots", filename=paste("compare_transforms_", strategy_filename, "_", exp_id_transform_one, "_", exp_id_transform_two, "_aggregated_outcomes_boxplot_paired_lines-test.png", sep=""), width=8, height=6, dpi=300)

```



## All Outcomes Disaggregated


### Boxplot `r transform_one`

```{r, echo=FALSE}

ggplot(df_all_outcomes_transform_one, aes(x=Outcome, y=Proportion)) + geom_boxplot() + geom_jitter(alpha = 0.15, width = 0.3) + coord_cartesian(ylim = c(0, 1)) + theme_bw() 

```

### Boxplot `r transform_two`

```{r, echo=FALSE}

ggplot(df_all_outcomes_transform_two, aes(x=Outcome, y=Proportion)) + geom_boxplot() + geom_jitter(alpha = 0.15, width = 0.3) + coord_cartesian(ylim = c(0, 1)) + theme_bw() 

```



\newpage


# Tests for equivalence, by paired Outcomes

## CC pairwise (`r transform_one` ~ `r transform_two`)

### Boxplot with Scatter points, Wilcoxon p-value annotation

```{r, echo=FALSE}

df_combined_cc <- data.frame(
    Index = c(seq.int(100), seq.int(100)),
    Representation = factor(c(rep(paste(transform_one), 100), rep(paste(transform_two), 100))),
    Outcome = factor(c(rep("CC", 200))),
    Proportion = c(df_transform_one_cc$Proportion, df_transform_two_cc$Proportion)
)

# re-level to change from default alphabetical ordering
df_combined_cc$Representation <- factor(df_combined_cc$Representation, levels=c(paste(transform_one), paste(transform_two))) 

cc_plot <- ggplot(df_combined_cc, aes(x=Representation, y=Proportion)) + 
  geom_boxplot() + 
  geom_jitter(alpha = 0.15, width = 0.3) + 
  coord_cartesian(ylim = c(0, 1)) + 
  theme_bw() + 
  labs(x="CC") + 
  stat_compare_means(paired=TRUE, label.x = 1.35, label.y = 0.5)
cc_plot

```

### Wilcoxon 

```{r, echo=FALSE}

wilcox.test(df_transform_one_cc$Proportion, df_transform_two_cc$Proportion, paired = TRUE, alternative = "two.sided", conf.int = TRUE, exact=FALSE)

```

### Boxplot with Paired Lines 

```{r, echo=FALSE}

ggplot(df_combined_cc, aes(x = Representation, y = Proportion)) +
    geom_boxplot(aes(fill = Representation)) +
        geom_point(aes(col = Representation), size = 0.1, stroke = 0, shape = 16) +
    geom_line(aes(group = Index), alpha = 0.2, col = "grey") +
  coord_cartesian(ylim = c(0, 1))  +
  stat_compare_means(paired=TRUE, label.x = 1.35, label.y = 0.95) +
    labs(title = paste(strategy, "Paired Parameter Study", sep=" "),
        subtitle = paste("Distribution of ", transform_one, " & ", transform_two, " CC Outcomes. [Exp IDs: ", exp_id_transform_one, ", ", exp_id_transform_two, "]", sep="")) +
  theme_minimal() +
  scale_fill_brewer(palette="Blues") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12),    # Center title position and size
    plot.subtitle = element_text(hjust = 0.5, size=10),            # Center subtitle
    plot.caption = element_text(hjust = 0, face = "italic") # move caption to the left
  ) +
  rremove("legend")

ggsave(path="plots", filename=paste("compare_transforms_", strategy_filename, "_", exp_id_transform_one, "_", exp_id_transform_two, "_CC_pairwise_boxplot_paired_lines-test.png", sep=""), width=8, height=6, dpi=300)

```



## CD pairwise (`r transform_one` ~ `r transform_two`)

### Boxplot with Scatter points, Wilcoxon p-value annotation

```{r, echo=FALSE}

df_combined_cd <- data.frame(
    Index = c(seq.int(100), seq.int(100)),
    Representation = factor(c(rep(paste(transform_one), 100), rep(paste(transform_two), 100))),
    Outcome = factor(c(rep("CD", 200))),
    Proportion = c(df_transform_one_cd$Proportion, df_transform_two_cd$Proportion)
)

# re-level to change from default alphabetical ordering
df_combined_cd$Representation <- factor(df_combined_cd$Representation, levels=c(paste(transform_one), paste(transform_two))) 

cd_plot <- ggplot(df_combined_cd, aes(x=Representation, y=Proportion)) + 
  geom_boxplot() + 
  geom_jitter(alpha = 0.15, width = 0.3) + 
  coord_cartesian(ylim = c(0, 1)) + 
  theme_bw() + 
  labs(x="CD") + 
  stat_compare_means(paired=TRUE, label.x = 1.35, label.y = 0.5)
cd_plot
```

### Wilcoxon 

```{r, echo=FALSE}

wilcox.test(df_transform_one_cd$Proportion, df_transform_two_cd$Proportion, paired = TRUE, alternative = "two.sided", conf.int = TRUE, exact=FALSE)

```

### Boxplot with Paired Lines 

```{r, echo=FALSE}

ggplot(df_combined_cd, aes(x = Representation, y = Proportion)) +
    geom_boxplot(aes(fill = Representation)) +
        geom_point(aes(col = Representation), size = 0.1, stroke = 0, shape = 16) +
    geom_line(aes(group = Index), alpha = 0.2, col = "grey") +
  coord_cartesian(ylim = c(0, 1))  +
  stat_compare_means(paired=TRUE, label.x = 1.35, label.y = 0.95) +
    labs(title = paste(strategy, "Paired Parameter Study", sep=" "),
        subtitle = paste("Distribution of ", transform_one, " & ", transform_two, " CD Outcomes. [Exp IDs: ", exp_id_transform_one, ", ", exp_id_transform_two, "]", sep="")) +
  theme_minimal() +
  scale_fill_brewer(palette="Blues") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12),    # Center title position and size
    plot.subtitle = element_text(hjust = 0.5, size=10),            # Center subtitle
    plot.caption = element_text(hjust = 0, face = "italic") # move caption to the left
  ) +
  rremove("legend")

ggsave(path="plots", filename=paste("compare_transforms_", strategy_filename, "_", exp_id_transform_one, "_", exp_id_transform_two, "_CD_pairwise_boxplot_paired_lines-test.png", sep=""), width=8, height=6, dpi=300)

```



## DC pairwise (`r transform_one` ~ `r transform_two`)

### Boxplot with Scatter points, Wilcoxon p-value annotation

```{r, echo=FALSE}

df_combined_dc <- data.frame(
    Index = c(seq.int(100), seq.int(100)),
    Representation = factor(c(rep(paste(transform_one), 100), rep(paste(transform_two), 100))),
    Outcome = factor(c(rep("DC", 200))),
    Proportion = c(df_transform_one_dc$Proportion, df_transform_two_dc$Proportion)
)

# re-level to change from default alphabetical ordering
df_combined_dc$Representation <- factor(df_combined_dc$Representation, levels=c(paste(transform_one), paste(transform_two))) 

dc_plot <- ggplot(df_combined_dc, aes(x=Representation, y=Proportion)) + 
  geom_boxplot() + 
  geom_jitter(alpha = 0.15, width = 0.3) + 
  coord_cartesian(ylim = c(0, 1)) + 
  theme_bw() + 
  labs(x="DC") + 
  stat_compare_means(paired=TRUE, label.x = 1.35, label.y = 0.5)
dc_plot
```

### Wilcoxon 

```{r, echo=FALSE}

wilcox.test(df_transform_one_dc$Proportion, df_transform_two_dc$Proportion, paired = TRUE, alternative = "two.sided", conf.int = TRUE, exact=FALSE)

```

### Boxplot with Paired Lines 

```{r, echo=FALSE}

ggplot(df_combined_dc, aes(x = Representation, y = Proportion)) +
    geom_boxplot(aes(fill = Representation)) +
        geom_point(aes(col = Representation), size = 0.1, stroke = 0, shape = 16) +
    geom_line(aes(group = Index), alpha = 0.2, col = "grey") +
  coord_cartesian(ylim = c(0, 1))  +
  stat_compare_means(paired=TRUE, label.x = 1.35, label.y = 0.95) +
    labs(title = paste(strategy, "Paired Parameter Study", sep=" "),
        subtitle = paste("Distribution of ", transform_one, " & ", transform_two, " DC Outcomes. [Exp IDs: ", exp_id_transform_one, ", ", exp_id_transform_two, "]", sep="")) +
  theme_minimal() +
  scale_fill_brewer(palette="Blues") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12),    # Center title position and size
    plot.subtitle = element_text(hjust = 0.5, size=10),            # Center subtitle
    plot.caption = element_text(hjust = 0, face = "italic") # move caption to the left
  ) +
  rremove("legend")

ggsave(path="plots", filename=paste("compare_transforms_", strategy_filename, "_", exp_id_transform_one, "_", exp_id_transform_two, "_DC_pairwise_boxplot_paired_lines-test.png", sep=""), width=8, height=6, dpi=300)

```

## DD pairwise (`r transform_one` ~ `r transform_two`)

### Boxplot with Scatter points, Wilcoxon p-value annotation

```{r, echo=FALSE}

df_combined_dd <- data.frame(
    Index = c(seq.int(100), seq.int(100)),
    Representation = factor(c(rep(paste(transform_one), 100), rep(paste(transform_two), 100))),
    Outcome = factor(c(rep("DD", 200))),
    Proportion = c(df_transform_one_dd$Proportion, df_transform_two_dd$Proportion)
)

# re-level to change from default alphabetical ordering
df_combined_dd$Representation <- factor(df_combined_dd$Representation, levels=c(paste(transform_one), paste(transform_two))) 

dd_plot <- ggplot(df_combined_dd, aes(x=Representation, y=Proportion)) + 
  geom_boxplot() + 
  geom_jitter(alpha = 0.15, width = 0.3) + 
  coord_cartesian(ylim = c(0, 1)) + 
  theme_bw() + 
  labs(x="DD") + 
  stat_compare_means(paired=TRUE, label.x = 1.35, label.y = 0.5)
dd_plot
```

### Wilcoxon 

```{r, echo=FALSE}

wilcox.test(df_transform_one_dd$Proportion, df_transform_two_dd$Proportion, paired = TRUE, alternative = "two.sided", conf.int = TRUE, exact=FALSE)

```

### Boxplot with Paired Lines 

```{r, echo=FALSE}

ggplot(df_combined_dd, aes(x = Representation, y = Proportion)) +
    geom_boxplot(aes(fill = Representation)) +
        geom_point(aes(col = Representation), size = 0.1, stroke = 0, shape = 16) +
    geom_line(aes(group = Index), alpha = 0.2, col = "grey") +
  coord_cartesian(ylim = c(0, 1))  +
  stat_compare_means(paired=TRUE, label.x = 1.35, label.y = 0.95) +
    labs(title = paste(strategy, "Paired Parameter Study", sep=" "),
        subtitle = paste("Distribution of ", transform_one, " & ", transform_two, " DD Outcomes. [Exp IDs: ", exp_id_transform_one, ", ", exp_id_transform_two, "]", sep="")) +
  theme_minimal() +
  scale_fill_brewer(palette="Blues") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12),    # Center title position and size
    plot.subtitle = element_text(hjust = 0.5, size=10),            # Center subtitle
    plot.caption = element_text(hjust = 0, face = "italic") # move caption to the left
  ) +
  rremove("legend")

ggsave(path="plots", filename=paste("compare_transforms_", strategy_filename, "_", exp_id_transform_one, "_", exp_id_transform_two, "_DD_pairwise_boxplot_paired_lines-test.png", sep=""), width=8, height=6, dpi=300)

```
